### 2025-04-10 backmatter/solutions.tex
Final changes to main files for first draft

Notice that
\begin{align}
    (p_i + p_j)^2 = 2 E_i E_j (1 - \cos\theta_{ij}) = \frac{1}{2}Q^2 x_i x_j (1 - \cos\theta_{ij})
    \,,
\end{align}
which by momentum conservation is
\begin{align}
    (q - p_{\overline{ij}})^2 = Q^2 - 2 Q E_{\overline{ij}} = Q^2(1 - x_{\overline{ij}}) = Q^2(x_i + x_j - 1).
\end{align}
where \(p_{\overline{ij}}\) is the momentum of the final state which is not \(i\) or \(j\)
%
--
%
for example, if \(i=q\) and \(j = g\), then \(\overline{ij} = \bar{q}\), while if \(i=q\) and \(j = \bar{q}\), then \(\overline{ij} = g\).

Equating these formulae quickly yields
\begin{align}
    \cos\theta_{ij} &= \frac{1}{x_i x_j} - \frac{2}{x_i} - \frac{2}{x_j} + 1
    ,
    \\
    \frac{m^2_{ij}}{Q^2} &= x_i + x_j - 1
    .
\end{align}

The Lorentz-invariant form of these equations can be quickly written by noting that \(x_i = 2 E_i/\sqrt{s} = \frac{2 p_i\cdot q}{q^2}\), since, in the center of mass frame, the photon has momentum \(q \reppedby \sqrt{s}(1,0,0,0)\).

@@

This was done in \Sec{eikonal-limit}, so let us do it in a slightly different way,
\begin{align}
    \dd \widetilde\Phi_n
    &=
    \prod_{i=1}^n
    \frac{\dd^{d-1}k_i}{2 E_i \le(2\pi\ri)^{d-1}}
    =
    \prod_{i=1}^{n-2}
    \frac{\dd^{d-1}k_i}{2 E_i \le(2\pi\ri)^{d-1}}
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \notag
    \times
    \frac{\dd^{d-1}k'}{2 E' \le(2\pi\ri)^{d-1}}
    \le(2 E'\,\le(2\pi\ri)^{d-1}\ri)
    \,
    \delta^{(d-1)}\le(k' - k_n - k_{n-1}\ri)
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \notag
    \times
    \frac{\dd^{d-1}k_{n-1}}{2 E_{n-1} \le(2\pi\ri)^{d-1}}
    \frac{\dd^{d-1}k_n}{2 E_n \le(2\pi\ri)^{d-1}}
    \\
    &=
    \dd\widetilde\Phi_{n-1}
    \,\,\,
    \times
    \,\,\,
    \frac{\dd^{d-1}k_{n-1}}{2 E_{n-1} \le(2\pi\ri)^{d-1}}
    \frac{\dd^{d-1}k_n}{2 E_n \le(2\pi\ri)^{d-1}}
    \,\,\,
    \le(2 E'\,\le(2\pi\ri)^{d-1}\ri)
    \,\,
    \delta^{(d-1)}\le(k' - k_n - k_{n-1}\ri)
    \label{eq:factor_phasespace}
    .
\end{align}
Any integration over \(\dd^{d-1} k'\) is completely auxiliary, but it allows us to match to the case where we have only \(n-1\) outgoing particles (where the \((n-1)^\text{th}\) outgoing particle has momentum \(k'\)).

@@

% ---------------------------------------
\Soln{Splitting Functions of the SM I: QED}{massless-qed}
% ---------------------------------------

@@

\begin{remarkbox*}{}{}
\textit{
    By taking derivatives with respect to \(a\), we obtain
    \begin{align}
        \frac{\partial}{\partial a}
        x^{-1 + \epsilon}
        =
        0
        =
        \frac{1}{a}
        \le(
            a^\epsilon \delta(x)
            +
            \sum_{n=0}^\infty
            \frac{\epsilon^n}{n!}
            \epsilon^n
            a
            \frac{\partial}{\partial a}
            \le[\frac{\ln^n(x)}{x}\ri]_+^{(0,a)}
        \ri)
        \,.
    \end{align}
    Matching powers of epsilon gives us
    \begin{align}
        \frac{\partial}{\partial a}
        \le[\frac{\ln^n(x)}{x}\ri]_+^{(0,a)}
        =
        \frac{\ln^n(a)}{a}
        \,,
    \end{align}
    which is simply a manifestation of the alternative distributional definition of plus-functions given in \Eq{extended_plus-fn} of Remark~\ref{rem:extended_definition} together with the fundamental theorem of calculus, as emphasized in Exercise~\ref{ex:plus-fn-derivative}.
}
\end{remarkbox*}

@@

% ---------------------------------------
\Soln{Substructure with Multiple Emissions}{ungroomed-me}
% ---------------------------------------

@@

    % Draw arrows
    \draw [arrow] (start) -- (pro1);
    \draw [arrow] (pro1) -- (pro2);
    \draw [arrow] (pro2) -- (dec1);
    \draw [arrow] (dec1) -- node[]{yes}(pro3);
    \draw [arrow] (pro3) -- (dec2);
    \draw [arrow] (dec2) -- node[]{yes}(stop);
    % Draw special arrows
    \draw [arrow] (dec1) --  node[anchor=west, above=2pt ] {no} ++(-8,0) |- (pro1);    \draw [arrow] (dec2) --  node[anchor=east, above=2pt ] {no} ++(8,0) |- (pro1);
\end{tikzpicture}
}
% Caption
    \caption[The basic code flow of our simple parton shower algorithm.]{The basic code flow of the parton shower algorithm described in \Prob{partonshower}.
    %
    The veto algorithm is only used when considering MLL effects and is skipped at LL.
    %
    The computations of the algorithm are shown in orange, the decisions of the algorithm in green, and the start and stop of the algorithm in red.}
    \label{fig:ps_codeflow}
\end{figure}

@@

%Similar arguments show that at LL, the subjet EEC within a jet initiated by a parton of type \(i\) is simply the corresponding particle-level EEC restricted to \(\chi > r^2 / 4\).
%%
%Expressing the EEC for such a jet as a jet function \(J^i(\chi, r; Q)\) as in \App{EEC:formal} and \Eq{eec_jet_fn_ll_1}, we write
%\begin{align}
%    J^i(\chi>0, r; Q)
%    &=
%    \frac{2 \as}{\chi}
%    \,
%    \Theta(\chi > r^2 /4)
%    \,
%    \sum_{ab}
%    \le(
%        \int_0^1 \dd z \, z (1-z) \,
%        P_{ab \leftarrow i}(z)
%    \ri)
%    \,
%    \le(
%        \frac{\alpha_s\le(2\,Q\sqrt{\chi}\ri)}
%        {\alpha_s\le(Q\,\Rjet\ri)}
%    \ri)
%    ^
%    {\frac{\hat{p}(m)}{2\pi\beta_0}}
%    _{f\leftarrow i}
%    .
%\end{align}

@@

In terms of the \(x_i\) the angle between partons \(i\) and \(j\) is given by
\begin{align}
    \cos\theta_{ij} = \frac{2}{x_i x_j} - \frac{2}{x_i} - \frac{2}{x_j} + 1
    \,,
\end{align}
as shown in \Prob{eetohadrons_kinematics}.

In terms of these variables, we may write the NLO EEC in integral form (away from \(\chi = 0\), if we neglect contact terms with \(i=j\)) as
\begin{align}
    \label{eq:ee2hadrons_EEC}
    \frac{\dd\Sigma_\text{EEC}}{\dd\chi}
    (\chi>0)
    =
    4\,
    \ascf
    \sum_{i<j}
    \int_0^1 \dd x_i
    &
    \int_{1-x_i}^1 \dd x_j
    \frac{x_q^2 + x_{\overline{q}}^2}{(1-x_q)_+(1-x_{\overline{q}})_+}
    \,\frac{x_i}{2}
    \,\frac{x_j}{2}
    \\
    &
    \notag
    \delta\le(
        \chi
        -
        \le(
            \frac{1}{x_i} + \frac{1}{x_j} - \frac{1}{x_i x_j}
        \ri)
    \ri)
    ,
\end{align}
where we have added an overall factor of \(2\) on the right-hand-side to write the sum over non-contact contributions as \(\sum_{i \neq j} = 2 \sum_{i < j}\), and we have used that \(E_i/Q = x_i / 2\).

>>>>

@@

This was done in \Sec{universal-features}, so let us do it in a slightly different way,
\begin{align}
    \dd \widetilde\Phi_n
    &=
    \prod_{i=1}^n
    \frac{\dd^{d-1}k_i}{2 E_i \le(2\pi\ri)^{d-1}}
    =
    \prod_{i=1}^{n-2}
    \frac{\dd^{d-1}k_i}{2 E_i \le(2\pi\ri)^{d-1}}
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \notag
    \times
    \frac{\dd^{d-1}k'}{2 E' \le(2\pi\ri)^{d-1}}
    \le(2 E'\,\le(2\pi\ri)^{d-1}\ri)
    \,
    \delta^{(d-1)}\le(k' - k_n - k_{n-1}\ri)
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \notag
    \times
    \frac{\dd^{d-1}k_{n-1}}{2 E_{n-1} \le(2\pi\ri)^{d-1}}
    \frac{\dd^{d-1}k_n}{2 E_n \le(2\pi\ri)^{d-1}}
    \\
    &=
    \dd\widetilde\Phi_{n-1}
    \,\,\,
    \times
    \,\,\,
    \frac{\dd^{d-1}k_{n-1}}{2 E_{n-1} \le(2\pi\ri)^{d-1}}
    \frac{\dd^{d-1}k_n}{2 E_n \le(2\pi\ri)^{d-1}}
    \,\,\,
    \le(2 E'\,\le(2\pi\ri)^{d-1}\ri)
    \,\,
    \delta^{(d-1)}\le(k' - k_n - k_{n-1}\ri)
    \label{eq:factor_phasespace}
    .
\end{align}
Any integration over \(\dd^{d-1} k'\) is completely auxiliary, but it allows us to match to the case where we have only \(n-1\) outgoing particles (where the \((n-1)^\text{th}\) outgoing particle has momentum \(k'\)).

@@

% ---------------------------------------
% \Soln{Splitting Functions of the SM I: QED}{massless-qed}
% ---------------------------------------

@@

\begin{remarkbox*}{}{}
\textit{
    By taking derivatives with respect to \(a\), we obtain
    \begin{align}
        \frac{\partial}{\partial a}
        x^{-1 + \epsilon}
        =
        0
        =
        \frac{1}{a}
        \le(
            a^\epsilon \delta(x)
            +
            \sum_{n=0}^\infty
            \frac{\epsilon^n}{n!}
            \epsilon^n
            a
            \frac{\partial}{\partial a}
            \le[\frac{\ln^n(x)}{x}\ri]_+^{(0,a)}
        \ri)
        \,.
    \end{align}
    Matching powers of epsilon gives us
    \begin{align}
        \frac{\partial}{\partial a}
        \le[\frac{\ln^n(x)}{x}\ri]_+^{(0,a)}
        =
        \frac{\ln^n(a)}{a}
        \,,
    \end{align}
    which is simply a manifestation of the alternative distributional definition of plus-functions given in \Eq{extended_plus-fn} of Remark~\ref{rem:extended-plus-definition} together with the fundamental theorem of calculus, as emphasized in \Exercise{plus-fn-derivative}.
}
\end{remarkbox*}

@@

% ---------------------------------------
% \Soln{Substructure with Multiple Emissions}{ungroomed-me}
% ---------------------------------------

@@

    % Draw arrows
    \draw [arrow] (start) -- (pro1);
    \draw [arrow] (pro1) -- (pro2);
    \draw [arrow] (pro2) -- (dec1);
    \draw [arrow] (dec1) -- node[]{yes}(pro3);
    \draw [arrow] (pro3) -- (dec2);
    \draw [arrow] (dec2) -- node[]{yes}(stop);
    % Draw special arrows
    \draw [arrow] (dec1) --  node[anchor=west, above=2pt ] {no} ++(-8,0) |- (pro1);    \draw [arrow] (dec2) --  node[anchor=east, above=2pt ] {no} ++(8,0) |- (pro1);
\end{tikzpicture}
}
% Caption
    \caption[The basic code flow of our simple parton shower algorithm.]{The basic code flow of the parton shower algorithm described in \Prob{parton-shower}.
    %
    The veto algorithm is only used when considering MLL effects and is skipped at LL.
    %
    The computations of the algorithm are shown in orange, the decisions of the algorithm in green, and the start and stop of the algorithm in red.}
    \label{fig:ps_codeflow}
\end{figure}

@@

%Similar arguments show that at LL, the subjet EEC within a jet initiated by a parton of type \(i\) is simply the corresponding particle-level EEC restricted to \(\chi > r^2 / 4\).
%%
%Expressing the EEC for such a jet as a jet function \(J^i(\chi, r; Q)\) as in \App{EEC:formal} and \Eq{eec_jet_fn_ll_1}, we write
%\begin{align}
%    J^i(\chi>0, r; Q)
%    &=
%    \frac{2 \as}{\chi}
%    \,
%    \Theta(\chi > r^2 /4)
%    \,
%    \sum_{ab}
%    \le(
%        \int_0^1 \dd z \, z (1-z) \,
%        P_{ab \leftarrow i}(z)
%    \ri)
%    \,
%    \le(
%        \frac{\alpha_s\le(2\,Q\sqrt{\chi}\ri)}
%        {\alpha_s\le(Q\,\Rjet\ri)}
%    \ri)
%    ^
%    {\frac{2 \hat{p}(m)}{\beta_0}}
%    _{f\leftarrow i}
%    .
%\end{align}

@@

First, let us record some kinematics.
%
Notice that
\begin{align}
    (p_i + p_j)^2 = 2 E_i E_j (1 - \cos\theta_{ij}) = \frac{1}{2}Q^2 x_i x_j (1 - \cos\theta_{ij})
    \,,
\end{align}
which by momentum conservation is
\begin{align}
    (q - p_{\overline{ij}})^2 = Q^2 - 2 Q E_{\overline{ij}} = Q^2(1 - x_{\overline{ij}}) = Q^2(x_i + x_j - 1).
\end{align}
where \(p_{\overline{ij}}\) is the momentum of the final state which is not \(i\) or \(j\)
%
--
%
for example, if \(i=q\) and \(j = g\), then \(\overline{ij} = \bar{q}\), while if \(i=q\) and \(j = \bar{q}\), then \(\overline{ij} = g\).

Equating these formulae quickly yields
\begin{align}
    \cos\theta_{ij} &= \frac{1}{x_i x_j} - \frac{2}{x_i} - \frac{2}{x_j} + 1
    ,
    \\
    \frac{m^2_{ij}}{Q^2} &= x_i + x_j - 1
    .
\end{align}
%
The Lorentz-invariant form of these equations can be quickly written by noting that \(x_i = 2 E_i/\sqrt{s} = \frac{2 p_i\cdot q}{q^2}\), since, in the center of mass frame, the photon has momentum \(q \reppedby \sqrt{s}(1,0,0,0)\).

In terms of the \(x_i\), we may therefore write the NLO EEC in integral form (away from \(\chi = 0\), if we neglect contact terms with \(i=j\)) as
\begin{align}
    \label{eq:ee2hadrons_EEC}
    \frac{\dd\Sigma_\text{EEC}}{\dd\chi}
    (\chi>0)
    =
    4\,
    \ascf
    \sum_{i<j}
    \int_0^1 \dd x_i
    &
    \int_{1-x_i}^1 \dd x_j
    \frac{x_q^2 + x_{\overline{q}}^2}{(1-x_q)_+(1-x_{\overline{q}})_+}
    \,\frac{x_i}{2}
    \,\frac{x_j}{2}
    \\
    &
    \notag
    \delta\le(
        \chi
        -
        \le(
            \frac{1}{x_i} + \frac{1}{x_j} - \frac{1}{x_i x_j}
        \ri)
    \ri)
    ,
\end{align}
where we have added an overall factor of \(2\) on the right-hand-side to write the sum over non-contact contributions as \(\sum_{i \neq j} = 2 \sum_{i < j}\), and we have used that \(E_i/Q = x_i / 2\).

### 2025-04-10 chapters/1-qcd.tex
Final changes to main files for first draft

Hidden in the chaos of hundreds of numbers -- masses, charges, decay rates -- lay a deep order glimpsed by Gell-mann and Zweig \cite{} in their quark model, and in the geometric theory of Yang and Mills \cite{}, which forged together into the theory of \gls{qcd}.
%
In radical defiance of the theorists of the previous generation, Politzer \cite{Politzer:1973fx} and Gross and Wilczek \cite{Gross:1973ju} discovered that QCD was one of the only quantum field theories invulnerable to the disparagements of their predecessors.
%
We had obtained a theory of the strong force;
%
a theory that overcame decades of confusion, and explained our unexpected observation of dozens of new particles.

@@

Luckily, Sterman and Weinberg discovered a way around the divergences of QCD \cite{Sterman:1977wj};
%
they predicted that the chess pieces of QCD at high energies, not unlike the water droplets spraying from a high pressure hose, should shower into \vocab{jets} each potentially containing dozens of particles or more.
%
The jets they predicted as proxies for the high energy quarks and gluons produced by colliding particles were soon measured \cite{}, and the explosion of experimental, phenomenological, and theoretical study of jets that followed solidified \gls{qcd} as our fundamental theory of the strong nuclear force.
%
It is not an exaggeration to say that the discovery of jets has been one of the most important developments in the history of our study of the natural world.

@@

\begin{figure}[]
    {
        \hspace{-1.7cm}
        \input{includes/timeline.tikz}
    }
    \caption{
        A rough timeline of the history of \gls{qcd}.
        %
        \sam{Not complete! Many particles, as well as QGP, missing! May want to change notation, e.g. for particle discoveries}
        %
        \sam{Noah recommends lines connecting things to dates...}
    }
    \label{fig:qcd-timeline}
\end{figure}

@@

    % Caption
    \caption{
        A cartoon depicting zooming in on the universe, beginning at the largest known scales and ending at some of the smallest -- the scales of \gls{qcd}.
        %
        The top row, from right to left, depicts galactic filaments, galaxies, and the solar system.
        %
        The middle row depicts terrestrial scales (right to left):
        %
        the earth, a hunk of iron, the magnetic domains within iron, and a single iron atom.
        %
        The bottom row depicts the scales of \gls{qcd} (right to left):
        %
        a proton, a jet, a partonic splitting, and a single quark.
    }
    % Figure Label
    \label{fig:picturebook_universe}
\end{sourcefigure}

% -----------------------------------
% Particles Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \centering
    \includegraphics[width=0.65\textwidth]{figures/picturebook/particles}
    % Caption
    \caption{
        Quarks, visualized as red, blue, and green spheres, are fundamental particles -- they are pointlike, as far as we know, and among the smallest known pieces of our universe.
    }
    % Figure Label
    \label{fig:picturebook_particles}
\end{sourcefigure}

@@

    % Caption
    \caption{
        Jets, collimated sprays of hadronic particles visualized as green cones, are formed when quarks (or gluons) are pushed out of their confines during a high-energy particle collision and undergo a cascading series of ``decays'' called the partonic cascade.
        % https://indico.cern.ch/event/492098/contributions/1169736/attachments/1356309/2050123/QCD2.pdf#page=21
    }

@@

    % Caption
    \caption{
        The goal of \emph{jet grooming} is to recover the information of high-energy jet substructure representing the physics of high energy quarks and gluons (visualized as dark, opaque lines, with darker colors/more opacity indicating higher energy) despite obfuscation from soft distortions (hadronization, detector effects) and additive contamination (pileup, underlying event).
    }

@@

    % Caption
    \caption{
        Energy-weighted correlators capture correlations between high-energy structures within jets, such as particles (purple/black lines) or subjets (purple cones).
        %
        The explicit example of the resolved 3-point energy correlators of \Chap{ewocs}, compute using real collider data, are shown as colored disks above the jet to visualize energy-weighted correlations at different angular scales.
        %
        The higher energy regions of the cartoon jet depicted here are represented by higher values of the associated resolved energy correlator, and darker colors in the associated colored disks.
    }
    % Figure Label
    \label{fig:picturebook_eventshapes}
\end{sourcefigure}

>>>>

Hidden in the chaos of hundreds of numbers -- masses, charges, decay rates -- lay a deep order glimpsed by Gell-mann \cite{Gell-Mann:1964ewy} and Zweig \cite{Zweig:1964ruk,Zweig:1964jf} in their quark model, and in the geometric theory of Yang and Mills \cite{Yang:1954ek}, which forged together into the theory of \gls{qcd}.
%
In radical defiance of the theorists of the previous generation, Politzer \cite{Politzer:1973fx} and Gross and Wilczek \cite{Gross:1973ju} discovered that QCD was one of the only quantum field theories invulnerable to the disparagements of their predecessors.
%
We had obtained a theory of the strong force;
%
a theory that overcame decades of confusion, and explained our unexpected observation of dozens of new particles.

@@

Luckily, Sterman and Weinberg discovered a way around the divergences of QCD \cite{Sterman:1977wj};
%
they predicted that the chess pieces of QCD at high energies, not unlike the water droplets spraying from a high pressure hose, should shower into \vocab{jets} each potentially containing dozens of particles or more.
%
The jets they predicted as proxies for the high energy quarks and gluons produced by colliding particles were soon measured \cite{Hanson:1975fe,Wiik:1979cq,Barber:1979yr,TASSO:1979zyf,PLUTO:1979dxn,JADE:1979rke,Ali:1979em,Hanson:1981em,Ali:2010tw}, and the explosion of experimental, phenomenological, and theoretical study of jets that followed solidified \gls{qcd} as our fundamental theory of the strong nuclear force.
%
It is not an exaggeration to say that the discovery of jets has been one of the most important developments in the history of our study of the natural world.

@@

\begin{figure}[]
    {
        \hspace{-1.7cm}
        \input{includes/timeline.tikz}
    }
    \caption[A rough timeline of the history of \gls{qcd}. \sam{incomplete}]
    {
        A rough timeline of the history of \gls{qcd}.
        %
        \sam{Not complete! Many particles, as well as QGP, missing! May want to change notation, e.g. for particle discoveries}
        %
        \sam{Noah recommends lines connecting things to dates...}
    }
    \label{fig:qcd-timeline}
\end{figure}

@@

    % Caption
    \caption[A cartoon of the ideas of renormaliztion, in the context of zooming in from the largest to the smallest scales of the universe.]{
        A cartoon depicting zooming in on the universe, beginning at the largest known scales and ending at some of the smallest -- the scales of \gls{qcd}.
        %
        The top row, from right to left, depicts galactic filaments, galaxies, and the solar system.
        %
        The middle row depicts terrestrial scales (right to left):
        %
        the earth, a hunk of iron, the magnetic domains within iron, and a single iron atom.
        %
        The bottom row depicts the scales of \gls{qcd} (right to left):
        %
        a proton, a jet, a partonic splitting, and a single quark.
    }
    % Figure Label
    \label{fig:picturebook_universe}
\end{sourcefigure}

% -----------------------------------
% Particles Section:
% -----------------------------------
\begin{sourcefigure}[t!]
    % Figure graphics
    \centering
    \includegraphics[width=0.65\textwidth]{figures/picturebook/particles}
    % Caption
    \caption[A visualization of quarks as fundamental particles within the proton.]{
        Quarks, visualized as red, blue, and green spheres, are fundamental particles contained within the proton.
        %
        This is only a visualization -- quarks are pointlike, as far as we know, and among the smallest known pieces of our universe.
    }
    % Figure Label
    \label{fig:picturebook_particles}
\end{sourcefigure}

@@

    % Caption
    \caption[A visualization of jets formed by ejecting a quark from a nucleon during high energy scattering.]{
        Jets, collimated sprays of hadronic particles visualized as green cones, are formed when quarks (or gluons) are pushed out of their confines during a high-energy particle collision and undergo a cascading series of ``decays'' called the partonic cascade.
        % https://indico.cern.ch/event/492098/contributions/1169736/attachments/1356309/2050123/QCD2.pdf#page=21
    }

@@

    % Caption
    \caption[A visualization of the low-energy contamination within jets, whose removal is the goal of jet grooming.]{
        The goal of \emph{jet grooming} is to recover the information of high-energy jet substructure representing the physics of high energy quarks and gluons (visualized as dark, opaque lines, with darker colors/more opacity indicating higher energy) despite obfuscation from soft distortions (hadronization, detector effects) and additive contamination (pileup, underlying event).
    }

@@

    % Caption
    \caption[A visualization of energy-weighted correlations capturing correlations between different high-energy structures within jets at different scales. \sam{incomplete, want bunch crossings rather than nuclei}]{
        Energy-weighted correlators capture correlations between high-energy structures within jets, such as particles (purple/black lines) or subjets (purple cones).
        %
        The explicit example of the resolved 3-point energy correlators of \Chap{ewocs}, compute using real collider data, are shown as colored disks above the jet to visualize energy-weighted correlations at different angular scales.
        %
        The higher energy regions of the cartoon jet depicted here are represented by higher values of the associated resolved energy correlator, and darker colors in the associated colored disks.
        %
        \sam{incomplete, want bunch crossings rather than nuclei}
    }
    % Figure Label
    \label{fig:picturebook_eventshapes}
\end{sourcefigure}
